Roster Review (Generic)

### 2019-06-04 rosterReview_generic.Rmd
Per position zar sketches

rosters_by_position %>% 
  filter(!is.na(manager)) %>% 
  group_by(position) %>% 
  count() %>% 
  ungroup() -> count_by_pos

rosters_by_position %>% 
  group_by(position) %>% 
  arrange(zar %>% desc()) %>% 
  mutate(num = row_number()) %>% 
  ungroup %>% 
  full_join(count_by_pos, "position") %>% 
  filter(num <= 1.5 * n) %>% 
  select(team, manager, name_full, position, zar) %>% View()
```

>>>>

rosters_by_position %>% 
  filter(!is.na(manager)) %>% 
  group_by(position) %>% 
  count() %>% 
  ungroup() -> rostered_count_by_pos

rosters_by_position %>% 
  group_by(position) %>% 
  arrange(zar %>% desc()) %>% 
  mutate(num = row_number()) %>% 
  full_join(rostered_count_by_pos, "position") %>% 
  filter(num <= n) %>% 
  summarize(median_zar = median(zar)) -> pos_median_zar

rosters_by_position %>% 
  full_join(pos_median_zar) %>% 
  mutate(pos_zar = zar + median_zar) -> rosters_by_position

rosters_by_position %>% 
  select(team, manager, name_full, position, zar, pos_zar) %>% 
  View()

rosters_by_position %>% 
  filter(team != "Free Agent") %>% 
  ggplot(aes(position, pos_zar, color = position, alpha = zar)) +
  geom_point(aes(text=name_full)) +
  facet_wrap(~ team) -> team_pos_adj

ggplotly(team_pos_adj)
